The SMT Competition 2015--2018

### 2019-08-27 2018/report/SMT-COMP.tex
Minor

Tables~\ref{table:participants1}-\ref{table:participants3} list the solvers
that participated between~2015 and~2018, together with contributing team
members (in alphabetical order) and their institutional affiliations (which may
have changed over time).

>>>>

Tables~\ref{table:participants1}--\ref{table:participants3} list the solvers
that participated between~2015 and~2018, together with contributing team
members (in alphabetical order) and their institutional affiliations (which may
have changed over time).
